Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-10-11 writeup/RochatEtal_ResponseToReviewers_BIS.tex

\maketitle

\section*{Summary}

\section{Reviewer \#1}

{\it The authors have adequately addressed all the questions raised in my
previous review. I recommend the manuscript be accepted for publication in GRL.}

\bdp
  \item We thank the reviewer for constructive review.
\edp

\section{Reviewer \#2}

{\it I have read the revised manuscript and the authors have adequately addressed
     my concerns. Here I would like to point out things I noticed.
     Please ignore those if you don't like.}

\bdp
   \item We thank the reviewer for constructive review.
\edp

@@

\begin{enumerate}

\item {\it Line 166. "super-inertial IGWs" I think IGW represents any oscillation whose
                frequency is between f and N. If so, super-inertial is not needed.}

\item {\it Line 174. "inertia gravity waves" should be IGWs.}

\item {\it Line 187. I am not sure if PSI is important near surface and wonder if it
                is resolved in this model because of the vertical resolution.
                Authors could discuss about PSI in the model with Jenn Mackinnon there.}

\item {\it Line 196. Remove "?"}

\item {\it In supplement, page x-3 first line. Remove "r"}

\item {\it To separate IGWs and other submesoscale motion, Ertel vorticity could be
      used (e.g. Kunze 1993, JPO, 2567-2588). This paper is about deep ocean though.}

### 2016-10-11 writeup/rocha_etal.tex
Adds reviewers reviwer2

Figure \ref{fig4}c shows the integral over frequency
of wavenumber-frequency spectra in figures \ref{fig4}a-b.
Both in April and October, the
SSH wavenumber spectrum approximately follows a -2 power-law at submesoscales
(solid lines in figure \ref{fig4}c)  --- there is
small difference between the spectra owing to the phase cancellation between the
seasonal cycle of submesoscale turbulence and inertia-gravity waves. The sub-inertial flow
has a steeper submesoscale SSH variance wavenumber spectrum (dashed lines in figure \ref{fig4}c).
 The difference between the SSH variance wavenumber spectrum for all frequencies and
 sub-inertial frequencies is dramatic in October when super-inertial flows account for
 about 80\% of the SSH variance and KE at submesoscales --- we obtain similar results by computing
SSH variance and KE wavenumber spectra directly from hourly and daily-averaged
SSH velocity fields.

>>>>

Figure \ref{fig4}c shows the integral over frequency
of wavenumber-frequency spectra in figures \ref{fig4}a-b.
Both in April and October, the
SSH wavenumber spectrum approximately follows a -2 power-law at submesoscales
(solid lines in figure \ref{fig4}c)  --- there is
small difference between the spectra owing to the phase cancellation between the
seasonal cycle of submesoscale turbulence and IGWs. The sub-inertial flow
has a steeper submesoscale SSH variance wavenumber spectrum (dashed lines in figure \ref{fig4}c).
 The difference between the SSH variance wavenumber spectrum for all frequencies and
 sub-inertial frequencies is dramatic in October when super-inertial flows account for
 about 80\% of the SSH variance and KE at submesoscales --- we obtain similar results by computing
SSH variance and KE wavenumber spectra directly from hourly and daily-averaged
SSH velocity fields.

### 2016-10-11 writeup/rocha_etal_supporting-info.tex
Adds reviewers reviwer2

For the LLC hierarchy, the sea-surface height is calculated
using a linearized equation. While the nominal horizontal resolution  of the
LLC4320 and LLC2160 simulations are 1/48$^\circ$ and 1/24$^\circ$, r
horizontal wavenumber spectra suggests an effective resolution of about 8 km and 20 km,
 respectively (see figure S1).

>>>>

For the LLC hierarchy, the sea-surface height is calculated
using a linearized equation. While the nominal horizontal resolution  of the
LLC4320 and LLC2160 simulations are 1/48$^\circ$ and 1/24$^\circ$,
horizontal wavenumber spectra suggests an effective resolution of about 8 km and 20 km,
 respectively (see figure S1).
